Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-19 paper.tex
Modificata Fig.2
ROC nuove!
Abstract e Section 1

\begin{document}
\title{Tampering Detection In Low-Power Smart Cameras}

@@

\begin{abstract}
A desirable feature in smart cameras is the ability to autonomously detect any tampering event/attack that would prevent a clear view over the monitored scene. No matter whether tampering is due to atmospheric phenomena (e.g., few rain drops over the camera lens) or to malicious attacks (e.g., the device displacement), these have to be promptly detected to possibly activate countermeasures. Tampering detection becomes particularly challenging in battery-powered cameras, where it is not possible to acquire images at full-speed  frame-rates, nor use sophisticated image-analysis algorithms.

We here introduce a tampering-detection algorithm specifically designed for low-power smart cameras: the algorithm leverages very simple indicators that are then monitored by an outlier-detection scheme. Any frame yielding anomalous indicator is detected as a tampered frame. Core of the algorithm is the partitioning of the scene into adaptively defined regions, that are preliminarily defined by segmenting the image during the algorithm-configuration phase, and which shows to improve the detection of camera displacements. Our experiments show that the proposed algorithm can successfully operate on sequences acquired at very low-frame rate, such as one frame every minute, with a very small computational complexity. %and leveraging the image partitioning into regions yields improved performance with respect to monitoring the whole scene
\keywords{tampering detection, blurring detection, displacement detection}
\end{abstract}

\section{Introduction}\label{sec:introduction}
% What is the problem?
When cameras operate outdoor and in harsh environments, dust, rain drops or snow flakes might lie on the camera lens resulting in blurry pictures, as shown in Figure \ref{fig:pioggia}, or in partial occlusions of the scene, as in Figure \ref{fig:neve}. Similarly, intentional attacks like displacing the camera, changing its focus, or spraying some opaque or glossy liquid over the lenses, would result in heavily compromised pictures, that would be useless for monitoring purposes. We refer to these events/attacks as tampering. In some cases, tampering is easy to detect, e.g., when the camera integrity is affected and the device goes out-of-order. However, in many other situations, namely when the device is not physically damaged, tampering detection is not straightforward, and sometimes image analysis is the only viable option.

@@

% Why is it interesting and important?
Tampering detection is an essential feature in surveillance systems~\cite{hampapur2005smart}, where cameras are expected to autonomously detect any tampering, and promptly report alerts. In fact, tampering prevents the correct interpretation of the scene: even a mild blur might hinder the identification of important details such as licence plates. Surveillance cameras are typically connected to the power supply and operate at normal frame-rates (e.g. around few frames per second): in these conditions, several tampering-detection algorithms have been presented. In particular, camera displacement and occlusions are typically detected by estimating the background or computing frame difference, while blurring is instead detected by monitoring the high-frequency components of images, as these are expected to drop. In~\cite{aksay2007camera} and~\cite{saglam2009real} tampering is detected by comparing histograms of background and current frame, and by monitoring the energy in wavelet or Fourier domain. Two background models, estimated over different time intervals, are used in~\cite{saglam2009real}. In~\cite{gil2007automatic}, tampering detection is performed by combining background subtraction together with edge detection and normalized cross-correlation. Background estimates and block matching in~\cite{tsesmelis2013tamper} enable the displacement detection, while the number of SURF~\cite{bay2006surf} keypoints is used to detect blurring. A frame buffer rather than an explicit background is used~\cite{ribnick2006real}. All these solutions, including~\cite{harasse2004automated,kryjak2012fpga} are computationally demanding, and are not viable options for low-power cameras.

In this work we expressly target low-power and ultra-low-power smart cameras, like \emph{SecSoC} (Security System on Chip), an innovative prototype based on a cluster of ReISC (Reduced Energy Instruction Set Computer) cores, designed and producted by STMicroelectronics, operating at clock rates of 82.5 MHz at 1.2V and sub-1MHz at 0.6V. These devices are battery-powered, and characterized by a constrained computational power and memory availability. While low-power cameras are typically not employed in critical surveillance applications, they are becoming popular in distributed systems for monitoring wide environments due to their low cost and maintenance requirements.  %As an example, consider Wireless Multimedia Sensor Networks (WMSN) \cite{akyildiz2007survey} where smart-cameras can acquire and transmit images at regular time interval or upon requests. 
% These units are not connected to the power supply and have to operate with batteries and possibly rely on energy harvesting~\cite{magno2009adaptive}. 
%In practice, because of energy constrain, low-power devices have to operate at very low frame-rates: possibly less than one frame every minute.

% Why is it hard? (E.g., why do naive approaches fail?)
Tampering detection in low-power smart cameras has not been much investigated in the literature~\cite{alippi2010detecting}, also because it is more challenging than in conventional surveillance cameras~\cite{perrig2004security}. Beside computational aspects -- such as the number of operations per pixels allowed -- the big issue is that low-power smart cameras typically operate at very low-frame rates (e.g., less than one frame per minute), thus the acquired sequence does not evolve smoothly. This prevents the use of learned background models and the analysis of foreground variations. In fact, when dynamic environments are acquired at low frame rates, two consecutive frames might be very different because of changes in the scene and in the light conditions, yielding sequences like those in Figure~\ref{fig:sequences}. Smart cameras have to promptly distinguish between \emph{normal} scene or illumination changes, and changes due to camera tampering to avoid the transmission of corrupted frames. Moreover, false alarms represent a serious problem in low-power smart cameras since they result in energy waste because of useless data processing and unnecessary network transmissions.
% We here address the problem of detecting tampering events on a camera device that is employed for monitoring purpose. Tampering events can be due to malicious attacks, as for instance a displacement of the camera or spraying some dirty liquid that would prevent the acquisition of (part of) the monitored scene or the interpretation of the content (e.g., the identification of licence plates).

%What are the key components of my approach and results? Also include any specific limitations.
We address the detection of camera blurring and displacement, which are presented in Section \ref{sec:probForm}. The proposed algorithm, detailed in Section~\ref{sec:propSol}, relies on two indicators: the average image intensity is used to detect displacement, and the average gradient norm to detect blurring. These indicators can be easily computed and monitored by an outlier-detection technique in a low-power smart camera. In particular, we show that separately monitoring the indicators over different regions of the image can substantially improve the displacement-detection performance. Remarkably, these regions can be preliminarily defined during an initial configuration phase (Section \ref{subsec:Segmentation}), thus the algorithm operates at a negligible computational overhead w.r.t. monitoring the whole image (Section \ref{subsec:coputationalComplexity}). Thus, our solution represents a prompt trigger that can be possibly combined with other sequential monitoring techniques. Experiments in Section \ref{sec:experiments} show that leveraging image regions can substantially improve the displacement-detection performance. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 3-rd frame, created using gaussian filtering; \textbf{(c)} displacement event on 3-rd frame, created moving the crop of the original image from the center.}
\label{fig:sequences}
\end{figure}

>>>>

\begin{document}
\title{Tampering Detection In Low-Power \\ Smart Cameras}

@@

\begin{abstract}
A desirable feature in smart cameras is the ability to autonomously detect any tampering event/attack that would prevent a clear view over the monitored scene. No matter whether tampering is due to atmospheric phenomena (e.g., few rain drops over the camera lens) or to malicious attacks (e.g., occlusions or the device displacement), these have to be promptly detected to possibly activate countermeasures. Tampering detection becomes particularly challenging in battery-powered cameras, where it is not possible to acquire images at full-speed  frame-rates, nor use sophisticated image-analysis algorithms.

We here introduce a tampering-detection algorithm specifically designed for low-power smart cameras: the algorithm leverages very simple indicators that are then monitored by an outlier-detection scheme. Any frame yielding anomalous indicator is detected as a tampered frame. Core of the algorithm is the partitioning of the scene into adaptively defined regions, that are preliminarily defined by segmenting the image during the algorithm-configuration phase, and which shows to improve the detection of camera displacements. Our experiments show that the proposed algorithm can successfully operate on sequences acquired at very low-frame rate, such as one frame every minute, with a very small computational complexity. %and leveraging the image partitioning into regions yields improved performance with respect to monitoring the whole scene
\keywords{tampering detection, smart cameras, displacement detection, blurring detection}
\end{abstract}

\section{Introduction}\label{sec:introduction}
% What is the problem?
When cameras operate outdoor and in harsh environments, dust, rain drops or snow flakes might lie on the camera lens resulting in blurry pictures, as shown in Figure \ref{fig:pioggia}, or in partial occlusions of the scene, as in Figure \ref{fig:neve}. Similarly, intentional attacks like displacing the camera Figure \ref{fig:pioggia} \gi{Adriano SISTEMA CON LE NUOVE FIGURE}, changing its focus, or spraying some opaque or glossy liquid over the lenses, would result in heavily compromised pictures, that would be useless for monitoring purposes. We refer to these events/attacks as tampering. In many situations, tampering is not straightforward to detect (e.g. when the camera is not physically damaged and does not go out-of-order), and image analysis techniques are the only viable option.

@@

% Why is it interesting and important?
Tampering detection is an essential feature in surveillance systems~\cite{hampapur2005smart}, where cameras are expected to autonomously detect any tampering, and promptly report alerts. In fact, tampering prevents the correct interpretation of the scene: for instance, even a mild blur might hinder the identification of important details such as licence plates. Surveillance cameras are typically connected to the power supply and operate at normal frame-rates (e.g. around few frames per second): in these conditions, several tampering-detection algorithms have been presented. In particular, camera displacement and occlusions are typically detected by comparing the current frame against an estimate of the scene background, while blurring is instead detected by monitoring the high-frequency components of images, as these are expected to drop. In~\cite{aksay2007camera} and~\cite{saglam2009real} tampering is detected by comparing histograms of background and current frame, and by monitoring the energy in wavelet or Fourier domain. Two background models, estimated over different time intervals, are used in~\cite{saglam2009real}. In~\cite{gil2007automatic}, tampering detection is performed by combining background subtraction together with edge detection and normalized cross-correlation. Background estimates and block matching in~\cite{tsesmelis2013tamper} enable the displacement detection, while the number of SURF~\cite{bay2006surf} keypoints is used to detect blurring. A frame buffer rather than an explicit background is used~\cite{ribnick2006real}. All these above solutions, including~\cite{harasse2004automated,kryjak2012fpga} are computationally demanding, and are not viable options for low-power cameras.

In this work we expressly target low-power and ultra-low-power smart cameras, like \emph{SecSoC} (Security System on Chip), an innovative prototype based on a cluster of ReISC (Reduced Energy Instruction Set Computer) cores, designed and produced by STMicroelectronics. SecSoC is a battery-powered device, characterized by a constrained computational power (clock rates 82.5 MHz at 1.2V, and sub-1MHz at 0.6V) and reduced memory (1.25 MB). While low-power cameras are not meant for critical surveillance applications, they might be easily employed in distributed systems for monitoring wide environments thanks to their low cost and maintenance requirements.  %As an example, consider Wireless Multimedia Sensor Networks (WMSN) \cite{akyildiz2007survey} where smart-cameras can acquire and transmit images at regular time interval or upon requests. 
% These units are not connected to the power supply and have to operate with batteries and possibly rely on energy harvesting~\cite{magno2009adaptive}. 
%In practice, because of energy constrain, low-power devices have to operate at very low frame-rates: possibly less than one frame every minute.

% Why is it hard? (E.g., why do naive approaches fail?)
Tampering detection in low-power cameras (eventually organized in wireless sensor network) is more challenging than in conventional surveillance systems, and this problem has not been much investigated so far~\cite{perrig2004security,alippi2010detecting}. Beside computational aspects -- such as the number of operations per pixels allowed -- the big issue is that low-power smart cameras typically operate at very low-frame rates (e.g., less than one frame per minute), thus the acquired sequence does not evolve smoothly. These aspects prevent the use of learned background models and the analysis of foreground variations. In fact, in dynamic environments are acquired at low frame rates, two consecutive frames might be very different because of changes in the scene and in the light conditions (see Figure~\ref{fig:sequences}). Smart cameras have then to promptly distinguish between \emph{normal} scene or illumination changes, and changes due to camera tampering to avoid the transmission of corrupted frames. %Moreover, false alarms represent a serious problem in low-power smart cameras since they result in energy waste because of useless data processing and unnecessary network transmissions.
% We here address the problem of detecting tampering events on a camera device that is employed for monitoring purpose. Tampering events can be due to malicious attacks, as for instance a displacement of the camera or spraying some dirty liquid that would prevent the acquisition of (part of) the monitored scene or the interpretation of the content (e.g., the identification of licence plates).

%What are the key components of my approach and results? Also include any specific limitations.
We address the detection of camera blurring and displacement, which are presented in Section \ref{sec:probForm}. The proposed algorithm (Section~\ref{sec:propSol}) relies on indicators that can be easily computed in low-power smart cameras, such as the average image intensity or frame difference (to detect camera displacement), and the average gradient norm (to detect blurring), and detects tampering as frames yielding outliers. In particular, we show that separately monitoring indicators over different regions of the image can substantially improve the displacement-detection performance. Remarkably, image regions can be preliminarily defined during an initial configuration phase (Section \ref{subsec:Segmentation}), thus the algorithm operates at a negligible computational overhead w.r.t. monitoring the whole image (Section \ref{subsec:coputationalComplexity}). Thus, our solution represents a prompt trigger that can be possibly combined with other sequential monitoring techniques. Experiments in Section \ref{sec:experiments} show that leveraging image regions can substantially improve the displacement-detection performance. % Concluding remarks and discussions are given in Section \ref{sec:Conclusion}.
\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 3-rd frame, created using gaussian filtering; \textbf{(c)} displacement event on 3-rd frame, created moving the crop of the original image from the center.}
\label{fig:sequences}
\end{figure}
